\section{Noise}
What is the level of noise in the expression of a single gene. 

synthetic biology: way to generate

quantifiable system. single copy chromosomal gene with an inducible promoter, in this way they could control the expression of these genes. Use of GFP, to measure fluorescence. IPTG to induce the promoter, various concentrations were used. Different stains with specific changes single based on the riosome bindin site and the initiation code, standardize the translational efficiency with the wild type.  Trascriptional control through mutations in the promoter and  number of plasmids to regulate trascription.

Measure fluorescence and same genetics and conditions, normal distribution. Flow citometry to measure fluorescence.

By producing the maximum amount of the protein (graph B), the noiser the output. Most of the noise derives from translational efficiency changes. 

Some genes ork better with log genetranslations.



Adaptive respponse of a gene network to ....

Cells alter gene expression, switching nutrient for example. Attractor states are multiparameter systems that tend to attract,. How cells are attracted. Some mechanisms permit the transition from a state to another, minimize U, hypothetical parameter of fitness.

Sensores, kinases and phosphorilases. evolutionary developed mechanism.

What about when the cells live in another completely new environment. 

completely or a mixture. glutamine sinthase because of differnet growth medium. wo chemicass that... express the correct operone and surbibe. monostable or bistable.

if changes the system, the attractor state is no more stable also. Nalidixic acid limits growth rate. In the two mediums, an operon chould be activated. 

started from a n intermadiate stae of fluorescence. Cells were able to change their genetic expression profile. 


2 possible explanations:

instruct the gene transcriprion apparatus to expres appropriate set of gene expression

Some cells 

experiments lasted for a low amount of time, to maintain  the same cells. 


In the opinion of researchers, scenarion 1 is necessary 


A decrease of cellular activity, and so it remains noise, and noise permits the cells to survive. These guys had the genes, but not actally expressing. 

Darwinian preadaptation

adaptability is not only a matter of time. sometimes it is possible that an advantageous situation is developed in a short time. 