\section{Presentation Stefano and Enrico}

Genetic circuits. navigate environment, produce chemicals and materials specific. 

genetic gates, logic gates familiar, and and nor gate. DNA binding protein used to implement. engineer a system sense a toxic metabolite, kept in a range which doesn't make the bacteria suffer.
bacteria to sense the pH.
Gene therapy circuits, smart plants, potential uses.

Current challenges: precise balancing of regulators, balance input and output. Balance strength of each promoter used. many gates stacked together. scalability also, big reactors, poo understanding of the system. measurement of circuit performance, chemical difficult to measure. 

Implement a and gate, PT7, when arabinose present, truncated polimers, only when tRNA Amber suppressor there is a tRNA . Coexpression is needed. 
2 strains used, complex media expensive complexes the lab cultures. another strain used in minimal environment. Scalability is a challenge. 

change growth and exxetera. how does the terrain components change funcitoning of the terrain. minima medium. the end gate functions better in LB, complex medium, expression similar to that of a plasmid. Not possible minimal terrains.
Industrial ancd controls in black. low results from the industrial strain, which is a problem

\delta G for 4 different \textit{rbs}, in different conditions, different magnitudes

laboratory to 1 mL bioreactor, 
arabinose, salicilate promoter is leaky and so arabiose activates the production of the protein.
Lievito only with both activated. 

3 strains + 1 of reference. 

and gates gives reduction in the biomass produced. 
loss of plasmids.

Genetic gates are viable in controlled and small scale environments, not extensive knowledge bout circuits. inconsistent output, noise. 

\section{Presentation tizie}
resistance plasmids give fitness benefits, 
